{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
Proof-read (rephrasings) of 4.2

Next, we can thus show how words are modified once we know they are substituted, \hbox{i.e.} how their features are modified by the said substitution.
We therefore measure how a word $\wstart$'s feature varies as $\wstart$ is substituted by $\warrival$, i.e. $\phi(\warrival)$ as a function of $\phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

Of prime interest is the comparison of the value of $\nu_{\phi}(f)$ with respect to $f$, as it shows whether there is an attraction (or repulsion) effect towards some values of each feature.  In other words, plotting the $y=x$ line, we can see if substitutions tend to converge towards some typical value of a word feature or not --- as is classically done in the study of dynamic systems.

@@

\medskip Results are gathered on Fig.~\ref{fig:feature-variations}.
 We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.  In other words, there exists a unique attractor for all features.  
Second, the comparison with $\mathcal{H}_0$ shows that we have two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.

>>>>

We can thus show how words are modified once we know they are substituted, \hbox{i.e.} how their features are modified by said substitution.
We therefore measure how a word $\wstart$'s feature varies as $\wstart$ is substituted for $\warrival$, i.e. $\phi(\warrival)$ as a function of $\phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

Of prime interest is the comparison of the value of $\nu_{\phi}(f)$ with respect to $f$, as it shows whether there is an attraction (or a repulsion) effect towards (resp. from) some values of each feature.
In other words, plotting the $y=x$ line, we can see if substitutions tend to converge towards some typical value of a word feature or not --- as is classically done in the study of dynamical systems.

@@

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.
In other words, each feature exhibits a unique attractor.  
Second, the comparison with $\mathcal{H}_0$ shows that there are two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.
